Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-10-24 paper-bedpca.tex
add method overview

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english, 12pt]{article}
\usepackage{times}
%\usepackage{algorithm2e}
\usepackage{url}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm}
\usepackage{rotating}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{bbm}

@@

\title{Efficient toolkit implementing best practices for principal component analysis of population genetic data}
\author{Florian Priv\'e,$^{\text{1,}*}$ John J. McGrath,$^{\text{1,2,3}}$ and Bjarni J. Vilhj\'almsson$^{\text{1,}*}$}

@@

>>>>

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english, 12pt]{article}
\usepackage{times}
%\usepackage{algorithm2e}
\usepackage{url}
\usepackage{bbm}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{geometry}
\geometry{verbose,letterpaper,tmargin=2cm,bmargin=2cm,lmargin=1.5cm,rmargin=1.5cm}
\usepackage{rotating}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{setspace}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{bbm}
\usepackage{makecell}

\renewcommand{\arraystretch}{2}

@@

\title{Efficient toolkit implementing best practices for principal component analysis of population genetic data}
\author{Florian Priv\'e,$^{\text{1,}*}$ Keurcien Luu, Michael G.B. Blum, John J. McGrath,$^{\text{1,2,3}}$ and Bjarni J. Vilhj\'almsson$^{\text{1,}*}$}

@@

\begin{table}[h]
\centering
\caption{Overview of existing methods. [TODO: ADD CITATIONS]} 
\label{tab:method-overview}
\begin{tabular}{|c|c|c|c|}
\hline
Analysis & Method / Software & Pros & Cons \\
\hline
\multirow{3}{*}{PCA} & bigstatsr / bigsnpr & \makecell{Fast and accurate + handle dosages \\ + thinning options directly included} & \makecell{Own format without missing values \\ (fast functions are available \\ for converting and imputing)} \\
 & FlashPCA2 & Fast and accurate & Not parallelised? \\
 & \makecell{PLINK 2.0 \\ (reimplementation of FastPCA)} & Very fast (AVX2 only?) & Not always 100\% accurate \\
\hline
\makecell{Detection of \\ oultier samples} & \makecell{"6 SDs from the mean" \\ (EIGENSOFT)} & Simple & Assume Gaussian distritbution \\
\hline
\makecell{Detection of \\ homogeneous \\ samples} & Aberrant & Robust & Only two statistics at once? \\
\hline
\multirow{5}{*}{\makecell{Projection of \\ new individuals \\ onto reference \\ PCA space}} & Simple projection (multiplication by loadings) & Simple & Shrinkage biased \\
  & Bias-adjusted projection & Independent of new samples & \makecell{Assume same shrinkage for all individuals \\ + model-based \\ + need all eigenvalues of reference} \\
  & \makecell{Augmentation, Decomposition, \\ and Procrustes transformation (ADP)} & Accurate & Slow \\
  & Online ADP (OADP) & Much faster than OADP & Does not work for related individuals \\ 
\hline
\end{tabular}
\end{table}
